Notebook of learning from ensemble labels

### 2021-05-21 docs/notebook_learn_dl_ensemble.Rmd
Update code to run in command line

#### Parameters setting
After successfully launched the instance, then it is ready to get into the instance to work.

@@

@@

###### DeepLab

>>>>

#### Instance setting
After successfully launched the instance, then it is ready to get into the instance to work.

@@

#### Run experiments

```
python hrlcm/fit.py --exp_name unet_single --data_dir 'results/north' --out_dir 'results/dl' --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
```

@@

##### DeepLab
